\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{xcolor}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ashwin KV} \\ \vspace{1pt}
    \small MERN Stack Developer \\
    \faPhone \hspace{1pt} +91 9567454484 $|$ 
    \href{mailto:ashwinkv.akv@gmail.com}{\faEnvelope \hspace{1pt} \color{blue}\underline{ashwinkv.akv@gmail.com}} $|$
    \faLinkedin \hspace{1pt} \href{https://www.linkedin.com/in/ashwin-kv/}{\color{blue}\underline{LinkedIn}} $|$
    \faGithub \href{https://github.com/dreamographer}{\color{blue}\underline{GitHub}} $|$
    \faGlobe \hspace{1pt} \href{https://leetcode.com/u/Ashwin_K_V/}{\color{blue}\underline{LeetCode}}
\end{center}

\vspace{-8pt}

\section{Summary}
Full Stack Developer with expertise in MERN stack and TypeScript, focused on building scalable web applications with clean architecture. Experienced in developing SaaS platforms and implementing modern development practices.

\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} JavaScript, TypeScript, SQL, HTML, CSS, Python, Java \\
     \textbf{Frameworks \& Libraries:} Express.js, Next.js, Nest.js, React, Redux Toolkit, Tailwind CSS \\
     \textbf{Databases \& Tools:} MongoDB, MySQL, PostgreSQL, Node.js, Git, Docker, AWS (EC2, S3, SQS), Socket.IO
    }}
\end{itemize}

\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Full Stack Developer}{Aug 2024 - Present}
{Finanshels}{Kozhikode, India}
\resumeItemListStart
\resumeItem{Developed and maintained core features using Next.js frontend and Nest.js/Express.js microservices backend architecture.}
\resumeItem{Implemented document management system and automated compliance workflows using TypeScript and PostgreSQL.}
\resumeItem{Built internal tools and automation systems including email integration, client onboarding, and ticket management.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
\resumeSubheading
{\textbf{Finanshels} - Financial Management SaaS}{Aug 2024 - Present}
{}{\color{blue}\underline{\href{https://www.finanshels.com/finanshels-app}{Live Link}}}
\resumeItemListStart
\resumeItem{Developed a comprehensive financial management platform using Next.js with responsive design.}
\resumeItem{Implemented document management system and Google Calendar integration for compliance tracking.}
\resumeItem{Built scalable application architecture using Next.js, Nest.js, Redux Toolkit, and PostgreSQL database.}
\resumeItemListEnd
\resumeSubheading
{\textbf{Finanshels Team} - Internal Management System}{Aug 2024 - Present}
{}{Internal Tool}
\resumeItemListStart
\resumeItem{Developed document collection and extraction system using Express.js, AWS SQS, and Gemini AI, reducing manual processing time by 60\% for CT registration process.}
\resumeItem{Implemented centralized mail system with Gmail integration and AWS S3-based document repository, enabling streamlined client communication history and document management.}
\resumeItem{Built comprehensive client onboarding system with automated notifications to Slack and email, including employee document management portal using React and Nest.js.}
\resumeItemListEnd
\resumeSubheading
{\textbf{ZenSync} - SaaS Application}{\color{blue}\underline{\href{https://www.zensync.ltd/}{Live Link}} \color{black} $|$ \color{blue}\underline{\href{https://github.com/dreamographer/zenSync-backend}{GitHub}}}
{}{}
\resumeItemListStart
\resumeItem{Developed a collaborative productivity platform with TypeScript, Next.js frontend, and Node.js/Express backend.}
\resumeItem{Implemented JWT authentication, Passport.js for OAuth, and real-time communication using Livekit SDK.}
\resumeItem{Utilized Zustand for state management and implemented Clean Architecture patterns.}
\resumeItemListEnd
\resumeSubheading
{\textbf{Offiq} - E-commerce Platform}{\color{blue}\underline{\href{https://www.offiq.shop/}{Live Link}} \color{black} $|$ \color{blue}\underline{\href{https://github.com/dreamographer/OFFIQ}{GitHub}}}
{}{}
\resumeItemListStart
\resumeItem{Built RESTful APIs using Node.js/Express for product listings, user authentication, and order management.}
\resumeItem{Integrated Razorpay payment gateway and MongoDB for efficient data management.}
\resumeItem{Developed comprehensive admin dashboard with analytics and reporting features.}
\resumeItem{Implemented advanced search, filter, and sorting functionalities for enhanced user experience.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{MERN Stack Development}{2023 - 2024}
{Brototype}{Trivandrum}
\resumeSubheading
{Bachelor of Computer Applications}{2020 - 2023}
{St. Aloysius College, Mangalore}{CGPA: 8.16}
\resumeSubHeadingListEnd

\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Head of Coding Event} - Composite 23, National Level IT Fest, St. Aloysius College \\
     \textbf{First Place} - Joshiana 11.0, National Level IT Fest, St. Joseph Engineering College \\
     \textbf{First Place} - Noesis 2023, National Level IT Fest, Rosary College
    }}
\end{itemize}

\end{document}
